Designing Types for R, Empirically

### 2020-05-16 paper/main.tex
Move simplification rules into a figure

\noindent
In other words, we take the union of the types occurring at individual
argument positions rather than an union of function types. Furthermore, we
apply some transformation on the types to keep the size of types in check.
The following overviews the main simplification rules as well as the simple
notion of subtyping that we have adopted here.

\vspace*{1mm}
\begin{tabular}{rclll}
  \T \k{~|~} \T  & $\Rightarrow$ &  \T &  \\
  \T \k{~|~} $T'$ & $\Rightarrow$ &  \T & \it{iff} $T' <: T$  \\
  \LIST{\T} \k{~|~} $\LIST{T'}$ & $\Rightarrow$ &  \LIST\T & \it{iff} $T' <: T$  \\
   $\null \k{~|~} \VEC{\S_1} \k{~|~}\dots \VEC{\S_n}$  & $\Rightarrow$ &
  $ \NAVEC{\S_1} \k{~|~}\dots \NAVEC{\S_n}$ &  \\
  \\
  \NAVEC\S  & <:& \VEC\S \\
  \T        & <:& \k{?}\T \\
  \LIST{\T} & <:& \LIST{\T'} & \it{iff} \T <: \T' \\
  \S        & <:& \VEC\S \\
  \lgl      & <:& \int\\
  \int      & <:& \dbl\\
  \dbl      & <:& \clx\\  
\end{tabular}
\medskip

\noindent
Assuming that type sequences can be reordered freely, we rewrite types to
minimize their size by removing redundant types, types that are subsumed by
subtyping, immutable lists, and remove \null type to replace them with
nullables. For performance reasons, we bound lists to no more than five
types in their union, above that they become \LIST{any}.  Functions are alos
limited to twenty arguments. Higher-order functions are approximated by \any
to \any.

@@

\begin{figure}[!h]\centering\includegraphics[width=.9\linewidth]
  {plots/corpus.pdf}\caption{Corpus}\label{fig:corpus}
\end{figure}

>>>>

\noindent
In other words, we take the union of the types occurring at individual argument
positions rather than an union of function types. Furthermore, we apply some
transformation on the types to keep the size of types in check.
Figure~\ref{fig:siplification-rules} overviews the main simplification rules as
well as the simple notion of subtyping that we have adopted here.

\begin{figure}[h!tb]
\begin{tabular}{rclll}
  \T \k{~|~} \T  & $\Rightarrow$ &  \T &  \\
  \T \k{~|~} $T'$ & $\Rightarrow$ &  \T & \it{iff} $T' <: T$  \\
  \LIST{\T} \k{~|~} $\LIST{T'}$ & $\Rightarrow$ &  \LIST\T & \it{iff} $T' <: T$  \\
   $\null \k{~|~} \VEC{\S_1} \k{~|~}\dots \VEC{\S_n}$  & $\Rightarrow$ &
  $ \NAVEC{\S_1} \k{~|~}\dots \NAVEC{\S_n}$ &  \\
  \\
  \NAVEC\S  & <:& \VEC\S \\
  \T        & <:& \k{?}\T \\
  \LIST{\T} & <:& \LIST{\T'} & \it{iff} \T <: \T' \\
  \S        & <:& \VEC\S \\
  \lgl      & <:& \int\\
  \int      & <:& \dbl\\
  \dbl      & <:& \clx\\  
\end{tabular}
\caption{Simplification rules and subtyping}
\label{fig:siplification-rules}
\end{figure}

Assuming that type sequences can be reordered freely, we rewrite types to
minimize their size by removing redundant types, types that are subsumed by
subtyping, immutable lists, and remove \null type to replace them with
nullables. For performance reasons, we bound lists to no more than five
types in their union, above that they become \LIST{any}.  Functions are alos
limited to twenty arguments. Higher-order functions are approximated by \any
to \any.

@@

\begin{figure}[!h]\centering\includegraphics[width=.8\linewidth]
  {plots/corpus.pdf}\caption{Corpus}\label{fig:corpus}
\end{figure}
